\documentclass{article}
\begin{document}
	\textbf{LITRATURE REVIEW ON FIREBASE}
	\section{Introduction}
Firebase is a technology that allows us to make web applications with no server-side programming so that development turns out to be easier and quicker. Using Firebase, we don’t have to stress over-provisioning servers or building REST APIs with just a very little configuration; 
\newline
\section{Functionality}
New numerous smart home advancements have been investigated and created. As the cloud computing is universal, there is one extend named a Framework for Cloud-based smart home.\cite{r1} In this project, they blend smart home into smart-home oriented cloud which simple extensible and fit for future demands. Also, the cloud give web administrations and the normal for smart home with six fundamental applications, which are security, environment, domestic, entertainment information, appliance, health and communication. Another \cite{r2}project called the Computer-supported design software for smart home device in view of cloud computing administration extend, helps designer select smart home device and assemble a smart living space.\cite{r6} This project also offers visual stimulation by applying the interface to build a genuine smart home. Besides, operation of smart home gadgets has four smart mode including responsive, passive, interactive and active. In this way, it is useful in quotes and budgeting. In Egypt,\cite{r7}there is a project called Energy sparing through smart home, means to utilize the sensors to minimize the domestic energy waste as indicated by human propensities and the proposed situation will likewise be accounted for of day by day schedule.
\newline
\section{Conclusion}
We can give Firebase a chance to take every necessary step: verifying users, storing data, and implementing access rules.
	
\bibliographystyle{IEEEtran}
\bibliography{documents}
\end{document}